SLT_paper

### 2020-08-04 SLT_paper.Rmd
broken, don't use

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(caret)

@@

```{r by child}

@@

zoon_sums = data_all %>% group_by(ChildID,Zoon_classif) %>% tally()
colnames(zoon_sums)<-c("ChildID",      "Zoon_classif", "n_zoo")
lab_sums = data_all %>% group_by(ChildID,lab) %>% tally()
zoon_sums$id=paste(zoon_sums$ChildID,zoon_sums$Zoon_classif)
lab_sums$id=paste(lab_sums$ChildID,lab_sums$lab)
sums=merge(zoon_sums,lab_sums[,c("lab" ,  "n", "id")],by="id",all=T)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(caret)
library(scales)

@@

```{r prepare data by child}

@@

## broken here!!
zoon_sums = data_all %>% group_by(ChildID,Zoon_classif, Age) %>% count(.drop = FALSE) #it's still dropping empty levels
colnames(zoon_sums)<-c("ChildID",      "Zoon_classif","Age", "n_zoo")
zoon_sums$id=paste(zoon_sums$ChildID,zoon_sums$Zoon_classif)
#add zeros
table(zoon_sums$ChildID,zoon_sums$Zoon_classif)==0
mytab=table(zoon_sums$ChildID,zoon_sums$Zoon_classif)
for(i in 1:dim(mytab)[1]) for(j in 1:dim(mytab)[2]) if(mytab[i,j]==0){
  zero_line=cbind(rownames(mytab)[i],colnames(mytab)[j],data_all[data_all$ChildID==rownames(mytab)[i],"Age"][1],0)
  colnames(zero_line)<-colnames(zoon_sums)
  zoon_sums=rbind(zoon_sums,
                zero_line)
}

lab_sums = data_all %>% group_by(ChildID, lab, Age) %>% count(.drop = FALSE)
lab_sums$id=paste(lab_sums$ChildID,lab_sums$lab)
sums=merge(zoon_sums,lab_sums[,c("lab", "Age" ,  "n", "id")],by="id",all=T)
sums$age=ifelse(!is.na(sums$Age.x),sums$Age.x,sums$Age.y)
summary(sums)

l_nl_z=zoon_sums$Zoon_classif

```{r corage}

plot()
